Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-11-18 docs/ms_sageAbundance.Rmd
adds new study area map with scale bar

\textsc{\small{Andrew T. Tredennick\footnote{Corresponding author: atredenn@gmail.com}\textsuperscript{1}, Mevin B. Hooten\textsuperscript{2,3,4}, Cameron L. Aldridge\textsuperscript{5}, Collin G. Homer\textsuperscript{6}, Andrew Kleinhesselink\textsuperscript{1}, and Peter B. Adler\textsuperscript{1}}}

@@

Figures
-------
```{r figure_1_alt,dependson="plot-options", fig.cap="Location of the 2.5 $\\times$ 5 kilometer study area in southwestern Wyoming and a snapshot of the percent cover data in 1984.", fig.height=6, eval=T}
library(png)
library(grid)
img <- readPNG("components/figure/studyarea_map.png")
grid.raster(img)
```

>>>>

\textsc{\small{Andrew T. Tredennick\footnote{Corresponding author: atredenn@gmail.com}\textsuperscript{1}, Mevin B. Hooten\textsuperscript{2,3,4}, Cameron L. Aldridge\textsuperscript{5}, Collin G. Homer\textsuperscript{6}, Andrew R. Kleinhesselink\textsuperscript{1}, and Peter B. Adler\textsuperscript{1}}}

@@

Figures
-------
```{r figure_1_alt,dependson="plot-options", fig.cap="Location of the 2.5 $\\times$ 5 kilometer study area in southwestern Wyoming (black rectangle) and a snapshot of the percent cover data in 1984 (detailed inset). Scale bar is relevant for US map only; refer to axes labels on the detailed inset of sagebrush percent cover for scale of the study area.", fig.height=6, eval=T}
library(png)
library(grid)
img <- readPNG("components/figure/studyarea_map.png")
grid.raster(img)
```
